Communication complexity: Chapter 6 \\ One-way communication and simultaneous message passing

### 2019-04-19 CS860-CommunicationComplexity/assignments/Chapter2.tex
Textbook wrapper

\documentclass[11pt]{amsart}
\usepackage{amsmath,amsthm,amsfonts,amssymb}
\usepackage{fullpage}
\usepackage[usenames]{xcolor}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{exercise}{Exercise}
\newtheorem{problem}{Problem}
\newtheorem{challenge}{Challenge Problem}
\newtheorem{open}{Open Problem}
\theoremstyle{plain}

\newcommand{\argmin}{\mathrm{argmin}}
\newcommand{\calX}{\mathcal{X}}
\newcommand{\calY}{\mathcal{Y}}
\newcommand{\calZ}{\mathcal{Z}}
\newcommand{\cost}{\mathrm{cost}}
\newcommand{\disc}{\mathrm{disc}}
\newcommand{\discu}{\mathrm{disc_u}}
\newcommand{\Disj}{\textsc{Disj}}
\newcommand{\Eq}{\textsc{Eq}}
\newcommand{\GT}{\textsc{GT}}
\newcommand{\IP}{\textsc{IP}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\replacethistext}[1]{\textcolor{red}{#1}}

\newcommand{\exercises}{\bigskip \noindent\rule{8cm}{0.4pt} \medskip}

\title{Communication complexity: Chapter 2 \\ More lower bound techniques}
\author{Eric Blais and Justin Toth}

\begin{document}

\maketitle

In the first chapter, we introduced the deterministic communication complexity 
model and saw the general \emph{partition bound} method for proving communication complexity lower bounds. While the partition bound is quite strong, it is hard to work with directly. The goal of this chapter is to introduce other general methods for proving communication complexity lower bounds more easily: the \emph{fooling set bound}, the \emph{rectangle size bound}, and the \emph{log rank bound}.

@@

\end{document}

>>>>

\chapter[Lower Bounds]{More Lower Bound Techniques}
In the first chapter, we introduced the deterministic communication complexity 
model and saw the general \emph{partition bound} method for proving communication complexity lower bounds. While the partition bound is quite strong, it is hard to work with directly. The goal of this chapter is to introduce other general methods for proving communication complexity lower bounds more easily: the \emph{fooling set bound}, the \emph{rectangle size bound}, and the \emph{log rank bound}.

@@

### 2019-04-19 CS860-CommunicationComplexity/assignments/Chapter6.tex
Textbook wrapper

\documentclass[11pt]{amsart}
\usepackage{amsmath,amsthm,amsfonts,amssymb}
\usepackage{fullpage}
\usepackage[usenames]{xcolor}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{exercise}{Exercise}
\newtheorem{remark}{Remark}
\newtheorem{problem}{Problem}
\newtheorem{challenge}{Challenge Problem}
\newtheorem{open}{Open Problem}
\theoremstyle{plain}

\newcommand{\argmin}{\mathrm{argmin}}
\newcommand{\calX}{\mathcal{X}}
\newcommand{\calY}{\mathcal{Y}}
\newcommand{\calZ}{\mathcal{Z}}
\newcommand{\cost}{\mathrm{cost}}
\newcommand{\dHam}{\mathrm{d}_{\mathrm{Ham}}}
\newcommand{\disc}{\mathrm{disc}}
\newcommand{\discu}{\mathrm{disc_u}}
\newcommand{\Disj}{\textsc{Disj}}
\newcommand{\Eq}{\textsc{Eq}}
\newcommand{\GHD}{\textsc{GHD}}
\newcommand{\GT}{\textsc{GT}}
\newcommand{\HD}{\textsc{HD}}
\newcommand{\ICext}{\mathrm{IC}^{\mathrm{ext}}}
\newcommand{\ICint}{\mathrm{IC}^{\mathrm{int}}}
\newcommand{\icostext}{\mathrm{icost}^{\mathrm{ext}}}
\newcommand{\icostint}{\mathrm{icost}^{\mathrm{int}}}
\newcommand{\IP}{\textsc{IP}}
\newcommand{\Index}{\textsc{Index}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\Rpriv}{R^{\mathrm{priv}}}
\newcommand{\replacethistext}[1]{\textcolor{red}{#1}}

\newcommand{\exercises}{\bigskip \noindent\rule{8cm}{0.4pt} \medskip}

\title{Communication complexity: Chapter 6 \\ One-way communication and simultaneous message passing}
\author{Eric Blais and Justin Toth}

\begin{document}

\maketitle

Every communication complexity question we have studied so far in this course have been set in the model where there are two players, Alice and Bob, who exchange bits with each other to compute functions on their joint inputs. This is of course not the only model of communication that is of interest---other models where we change the number of parties or restrict how messages can be sent between them have also been studied extensively. In this chapter, we examine the communication complexity of functions when the communication between Alice and Bob is restricted.

@@

\bigskip
\noindent \emph{Hint.} By using (basic but still remarkable) results from error-correcting codes, it is sufficient to design a randomized protocol that computes the partial function $\Eq^* : \{0,1\}^n \times \{0,1\}^n \to \{0,1,*\}$ defined by
\[
\Eq^*(x,y) = \begin{cases}
1 & \mbox{if } x = y \\
0 & \mbox{if } \dHam(x,y) = \frac n2 \\
* & \mbox{otherwise}
\end{cases}
\]
with error at most $\frac13$.
\end{document}

>>>>

\chapter[One-way Communication and SMP]{One-way Communication and Simultaneous Messsage Passing}
Every communication complexity question we have studied so far in this course have been set in the model where there are two players, Alice and Bob, who exchange bits with each other to compute functions on their joint inputs. This is of course not the only model of communication that is of interest---other models where we change the number of parties or restrict how messages can be sent between them have also been studied extensively. In this chapter, we examine the communication complexity of functions when the communication between Alice and Bob is restricted.

@@

\bigskip
\noindent \emph{Hint.} By using (basic but still remarkable) results from error-correcting codes, it is sufficient to design a randomized protocol that computes the partial function $\Eq^* : \{0,1\}^n \times \{0,1\}^n \to \{0,1,*\}$ defined by
\[
\Eq^*(x,y) = \begin{cases}
1 & \mbox{if } x = y \\
0 & \mbox{if } \dHam(x,y) = \frac n2 \\
* & \mbox{otherwise}
\end{cases}
\]
with error at most $\frac13$.
